\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2017-07-20 zfinalsubmission/FinalDraft-UMEM_CoSim.tex
final touches to paper

\linenumbers

@@

The first two objectives have been demonstrated in a simplified context in
previous literature \citep{thomas_customizable_2012,miller_long_2015}. The innovation
in the current publication is an extension of this research through the
modeling and co-simulation of real-world case studies. With respect to the
third contribution, to the best of the authors' knowledge, no previous study
has compared the results of a building and urban-scale co-simulation procedure
to measured data from a real-world campus.% \noteDT{:)}

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between
simulation engines at various scales. Much of the initial co-simulation work
in the literature is done at the subsystem and building-scale. Previous studies
have analyzed strong and loose coupling of engines at this scale
\citep{wetter_co-simulation_2011,trcka_co-simulation_2010}. Coupling of building-scale simulation with
urban-scale computational fluid dynamics (CFD) is attempted for modeling
natural ventilation \citep{zhang_coupled_2013} and to improve energy prediction
\citep{bouyer_microclimatic_2011}. A comprehensive review of energy and airflow modeling
of neighborhoods and university campuses was published that includes
strategic aspects of coupling different %\noteDT{did you mean: "strategic"?}b
types of models \citep{srebric_building_2015}. EnergyPlus has been coupled with ENVI-
met, a micro-climate computational fluid dynamics (CFD) program
\citep{yang_integrated_2012}. It was also coupled with simplified lumped parameter
models to facilitate comparison with measured sensor data
\citep{martin_estimation_2015}. While not directly coupled, EnergyPlus and the TEP Urban Canopy Model program were connected
through a modified weather file to quantify the influences of urban localized weather effects
on whole building simulation \citep{bueno_combining_2011}.

>>>>

@@

The first two objectives have been demonstrated in a simplified context in
previous literature \citep{thomas_customizable_2012,miller_long_2015}. The innovation
in the current publication is an extension of this research through the
modeling and co-simulation of real-world case studies. With respect to the
third contribution, to the best of the authors' knowledge, no previous study
has compared the results of a building and urban-scale co-simulation procedure
to measured data from a real-world campus.

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between
simulation engines at various scales. Much of the initial co-simulation work
in the literature is done at the subsystem and building-scale. Previous studies
have analyzed strong and loose coupling of engines at this scale
\citep{wetter_co-simulation_2011,trcka_co-simulation_2010}. Coupling of building-scale simulation with
urban-scale computational fluid dynamics (CFD) is attempted for modeling
natural ventilation \citep{zhang_coupled_2013} and to improve energy prediction
\citep{bouyer_microclimatic_2011}. A comprehensive review of energy and airflow modeling
of neighborhoods and university campuses was published that includes
strategic aspects of coupling different 
types of models \citep{srebric_building_2015}. EnergyPlus has been coupled with ENVI-
met, a micro-climate computational fluid dynamics (CFD) program
\citep{yang_integrated_2012}. It was also coupled with simplified lumped parameter
models to facilitate comparison with measured sensor data
\citep{martin_estimation_2015}. While not directly coupled, EnergyPlus and the TEP Urban Canopy Model program were connected
through a modified weather file to quantify the influences of urban localized weather effects
on whole building simulation \citep{bueno_combining_2011}.
